50. User-based: Run  this test to select best k for data set with cross validation. (use val data sets)
51. User-based: Run this test for k and y 2D test to detect if there is a correlation between k and y values. (use val datasets)

54. UB-LSH: Run this test 2D test to detect if there is a correlation between HashFunctions and k. (use val data sets)

55. UB-LSH: Run this test 2D test to detect if there is a correlation between HashFunctions and y. (Use best k value from test 54 and val data sets).

60. UB-LSH: Run this test 2D test to detect if there is a correlation between HashTables and k. (use val data sets, and HashFunctions and y from 54 and 55)

61. UB-LSH: Run this test 2D test to detect if there is a correlation between HashTables and y. (Use best k value from test 54 and val data sets)

59. Use the best k and y values from (54, 55) and run this test to find out how HashFunctions and Tables effect accuracy. (use val sets) Used k = 20 and y = 5

56. Select best HashFunctions from 59 then run this test to see prediction accuracy and HashTables change. (use test data sets)

57. Select best  HashTables from 59 and run this test to see prediction accuracy and HashFunctions change. (use test data sets)

58. Run this test with optimum HashFunctions and HashTables set to see the effect of increasing k on accuracy.

72. UB-LSH: Run this test to see relationship between k and HashFunctions

73. UB-LSH: Run this test to see relationship between k and HashTables


Test 50-51-58-62:

We run 2D tests for UB prediction and found out how k and y changes effect User-based accuracy (MAE).
from ml-mae-k-y-runtime-heat-map.eps we see that y and k are independent from each other. If we select
k too low or y too high that will decrease the accuracy. We will use these values for user-based tests.


k and y have different effect on LSH. based algorithms.

1. MAE and k

50-58 : MAE and k
51-62 : MAE and y

Detected optimum k and y values. k is best around 20-25 and y is best around 10 for UB and 4 for LSH.
Note that increasing y improves MAE first and if we keep to increase y this effects MAE in a negative way.
We have run cross validation for k and y changes no correlation!



Test 54-55-60-61 :
We run 2D tests for UB-LSH to find out how k, y and Hash Functions and Tables effect the accuracy.
We found out that no correlation between hash functions, tables and k nor y.
 No surprise.


Test 59: Use optimum k and y and run 2D UBLSH test for lower and upper bounds of HashTables/Functions
When we increase hash functions we need to increase hash tables too to preserve MAE in  certain range.
Draw 1D hash table and function graphs on MAE. Beyond max number of hash functions predictions error increases.


Test 70-71: UB and UBLSH precision against k. As expected precision increased as we increased k parameter.

Test 72: UBLSH precision and k and hash functions.
Precision increases as k increase and decreases as number of hash functions increased. (ymusic)





